Distributed Topology Discovery in Self-Assembled Nano Networks

### 2014-02-13 trunk/PAPER/implementation.tex
implementation update

In order to have an idea of the maximum working clock frequency for the
implemented circuitry, we can obtain the timing results from a gate-
level netlist. Since a complete technology library usefull for 
commercial synthesis tool (like Design Compiler) doesn't exist for the this particular technology
(at the best that we know), we have synthesized the RTL description of DiSR
with a standard 32nm CMOS library obtain 
a delay of about $\mathrm{\tau_{DiSR}=10} FO4$ (fan-out of four).
Considering the results obtained in~\cite{deng_isscc07}, wich reports the
ratio in therms of FO4 between a standard 32nm CMOS technology and a
carbon nanotube ones, we can have a rough delay estimation.
In particolar has been reported a ratio R of: 
\begin{equation}
\mathrm{R=\frac{FO4_{CMOS}}{FO4_{CNFET}}=2} 
\end{equation}
Considering that F04 CMOS is about 30 ps, and the results of  
last equation thedelay of one FO4 for the CNFET case is about of
15 ps an then the working frequency can be cmputed as:

@@

Regards the power
consumption of the entire DiSR devices, we can skip to perform an a

>>>>

In order to have an idea of the maximum working clock frequency for the
implemented circuitry, we can obtain the timing results from a gate-
level netlist. Since a complete technology library usefull for 
commercial synthesis tool (like Design Compiler) doesn't exist for the this particular technology
(at the best that we know), we have synthesized the RTL description of DiSR
with a standard 32nm CMOS library obtaining 
a delay of about $\mathrm{\tau_{DiSR}=10} FO4$ (fan-out of four).
Considering the results obtained in~\cite{deng_isscc07}, wich reports the
ratio in therms of FO4 between a standard 32nm CMOS technology and a
carbon nanotube ones, we can have a rough delay estimation.
In particolar has been reported a ratio R of: 
\begin{equation}
\mathrm{R=\frac{FO4_{CMOS}}{FO4_{CNFET}}=2} 
\end{equation}
Considering that F04 CMOS is about 30 ps, and the results of  
last equation thedelay of one FO4 for the CNFET case is about of
15 ps an then the working frequency can be computed as:

@@

Regards the power
consumption of the entire DiSR devices, we can skip to perform an accurate
power analysis with the switch activity annotation because the DiSR circuitry
will be active only once a time a the system startup. Indeed, after the setup
phase when all segments are mapped in to the network, the DiSR block will stop
its activity giving as output the fixed status of segments to the routing
algorithm. For this reason the dynamic power will goingo to zero and the only
cosumption will be eventually only due to the leackage consumption.
